### 2022-07-06 supplemental/OJEMB Supplementary Material.tex
Add to supplemental info

\begin{enumerate}
  \item \textit{Bernoulli}: A binned method in which each tonotopic bin
  has a probability $p$ of being set to $0$ dB otherwise it is set to $-20$ dB.
  \item \textit{Brimijoin}: A binned method inspired by \cite{brimijoinInternalRepresentationVowel2013}.
  Each bin is assigned an amplitude value chosen from a uniform distribution of discrete values
  on the interval $[-20, 0]$. We used $6$ steps, which is consistent with the original paper.
  \item \textit{Gaussian Noise No Bins}: The amplitude of each frequency was determined by
  Gaussian noise with known mean and variance, which are hyperparameters $\mu$ and $\sigma$.
  \item \textit{Gaussian Noise}: A binned method where the bin amplitudes were
  determined by a Gaussian random variable with known mean and variance, \eg $\mathcal{N}(\mu, \sigma)$.
  \item \textit{Gaussian Prior}: A binned method where the number of filled bins
  was set by $\mathrm{round}(\mathcal{N}(\mu, \sigma))$,
  and that many bins were filled randomly at $0$ dB (unfilled bins were set to $-20$ dB).
  \item \textit{Power Distribution}: A binned method where the amplitude of each bin
  is drawn from a distribution matching the histogram of amplitudes
  of the American Tinnitus Association tinnitus examples from their website.
  \item \textit{Uniform Noise No Bins}: The amplitude associated with each frequency
  is determined by a uniform random variable on the interval $[-20, 0]$ dB.
  \item \textit{Uniform Noise}: The amplitude associated with each tonotopic bin
  is determined by a uniform random variable on the interval $[-20, 0]$ dB.
  \item \textit{Uniform Prior}: The number of filled bins is determined by drawing an integer
  from the discrete interval $[x_1, x_2] \in \mathbb{Z}^+$. Then, that many bins are set to $0$ dB,
  and all other bins are set to $-20$ dB. $x_1$ and $x_2$ are hyperparameters.
\end{enumerate}

9 methods and 8 hyperparameters were varied in the hyperparameter sweep grid search.
Methods were evaluated \textit{in-silico} using the model:

@@

\begin{table}[ht]
	\begin{center}	
		\small
		\resizebox{1\columnwidth}{!}{
			\begin{tabular}{ m{0.35\columnwidth} m{0.65\columnwidth} }	
				\multicolumn{2}{c}{\textsc{Units for Magnetic Properties}} \\
				\hhline{===}
				{Symbol} & {Quantity} \\
				\hhline{===}

			\end{tabular}
		}
	\end{center}
\end{table}

>>>>

\begin{enumerate}
  \item \textit{Bernoulli}: A binned method in which each tonotopic bin
  has a probability $bin \_ prob$ of being set to $0$ dB otherwise it is set to $-20$ dB.
  \item \textit{Brimijoin}: A binned method inspired by \cite{brimijoinInternalRepresentationVowel2013}.
  Each bin is assigned an amplitude value chosen from a uniform distribution of discrete values
  on the interval $[-20, 0]$. We used $6$ steps, which is consistent with the original paper.
  \item \textit{Gaussian Noise No Bins}: The amplitude of each frequency was determined by
  Gaussian noise with known mean and variance, which are hyperparameters $amplitude \_ mean$ and $amplitude \_ var$.
  \item \textit{Gaussian Noise}: A binned method where the bin amplitudes were
  determined by a Gaussian random variable with known mean and variance, \eg $\mathcal{N}(amplitude \_ mean$ and $amplitude \_ var)$.
  \item \textit{Gaussian Prior}: A binned method where the number of filled bins
  was set by $\mathrm{round}(\mathcal{N}(n \_ bins \_ filled \_ mean, n \_ bins \_ filled \_ var))$,
  and that many bins were filled randomly at $0$ dB (unfilled bins were set to $-20$ dB).
  \item \textit{Power Distribution}: A binned method where the amplitude of each bin
  is drawn from a distribution matching the histogram of amplitudes
  of the American Tinnitus Association tinnitus examples from their website.
  \item \textit{Uniform Noise No Bins}: The amplitude associated with each frequency
  is determined by a uniform random variable on the interval $[-20, 0]$ dB.
  \item \textit{Uniform Noise}: The amplitude associated with each tonotopic bin
  is determined by a uniform random variable on the interval $[-20, 0]$ dB.
  \item \textit{Uniform Prior}: The number of filled bins is determined by drawing an integer
  from the discrete interval $[min \_ bins, max \_ bins] \in \mathbb{Z}^+$. Then, that many bins are set to $0$ dB,
  and all other bins are set to $-20$ dB. $min \_ bins$ and $max \_ bins$ are hyperparameters.
\end{enumerate}

9 methods and 8 hyperparameters were varied in the hyperparameter sweep grid search (Table \ref{tbl:hyperparameters}).
Methods were evaluated \textit{in-silico} using the model:

@@

\begin{table}[ht]
	\begin{center}	
		\small
		\resizebox{1\columnwidth}{!}{
			\begin{tabular}{ m{0.35\columnwidth} m{0.5\columnwidth} b{0.15\columnwidth}}	
				\multicolumn{3}{c}{\textsc{Hyperparameters}} \\
				\hhline{===}
				{Name} & {Values} & Unit \\ 
				\hline
				n\textunderscore bins & 10, 30, 100, 200, 300 & n.d. \\
				bin\textunderscore prob & 0.1, 0.3, 0.5, 0.8 & n.d. \\
                amplitude\textunderscore mean & -35 & dB \\
                amplitude\textunderscore var & 5, 10, 20 & $\sqrt{\mathrm{dB}}$ \\
                n\textunderscore bins\textunderscore filled \textunderscore mean & 1, 3, 10, 20, 30 & n.d. \\
                n\textunderscore bins\textunderscore filled\textunderscore var & 0.01, 1, 3, 10 & n.d. \\
                min\textunderscore bins & 1, 3, 10, 20, 30 & n.d. \\
                max\textunderscore bins & 10, 20, 30, 50 & n.d. \\
				\hhline{===}
			\end{tabular}
		}
	\end{center}
%\normalsize
	\caption{Hyperparameter values tested in the parameter sweep. Not all methods use all hyperparameters,
    and some combinations of hyperparameters are invalid (\eg when $min\_ bins > max \_ bins$).
    n.d. means ``non-dimensional'' and refers to a unitless number.
    }
	\label{tbl:hyperparameters}
\end{table}

Reconstructions were computed using linear regression and compressed sensing
and reconstruction accuracy was measured using Pearson's $r^2$ vs. the target signal.
